Goes Here

### 2012-07-28 paper.tex
Experiments

\section{Introduction}

\section{Conclusion}
\section*{Acknowledgements}

>>>>

\section{Introduction}
\section{System Description}
\subsection{Input API}
Specification of an optimization problem using our API.
\subsection{Optimization Framework}
Describe four main components and some built-in libraries.
\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
\subsection{Textured Model}
Input: a textured 3D model and
	measured Albedo of print material.

Output: (Probably gray-scale) Material arranged for different printers in different formats: STL, fable,Gcode.

Printers: Our printer, Makerbot, Objet, maybe Zcorp.

\subsection{New Examples for Mechanical Properties}
Ball bounce to certain height. Loaded dice.

Printer:objet, ours.

\section{Possible Extension}
UI to specify input deformation.
\section{Conclusion}
\section*{Acknowledgements}
